---
title: "TradeOff_survival_growth"
author: "Amaïa Lamarins"
date: "1/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Growth-survival trade-off

A growth survival trade-off have been implemented by J. Papaïx to limit individual growth. There is the possibility to parametrize it in river as well as in sea, but only the river one has been adjusted.

Here is the trend of the trade-off in river:

```{r, echo=FALSE}

pow <- function(x,y) {x^y}

coefSURV=function(pGres, kappaRIV, sigRIV) {(exp(-kappaRIV*pow(pGres,sigRIV))-exp(-kappaRIV))/(1-exp(-kappaRIV))}

# trade_off
maxRIV=5 # maxRIV maximum growth rate, aded for the incorporation of trade-off growth/survival
sigRIV=3.7 #10 # sigRIV shape of the trade-off function
kappaRIV=0.001 #921.6 # kappaRIV shape of the trade-off function

# Growth potential
#pG=sort(rnorm(10000,0,0.25))
pG=sort(runif(1000,-1,1))
pGres=exp(pG)/maxRIV;
pGres=ifelse(pGres>1,1,pGres)

plot(pG,coefSURV(pGres, kappaRIV, sigRIV),type='l',ylab="Survival coefficient",xlab="Growth potential",main="River trade-off",xlim=c(-1,1))
#lines(pG,coefSURV(pGres, kappaRIV, sigRIV2), col="red", type="l")


```

Here is the trend of the trade-off in sea:

```{r, echo=FALSE}
maxSEA=50 # no trade-off
sigSEA=100
kappaSEA=0.001

# Growth potential
#pG=sort(rnorm(10000,0,0.25))
pG=sort(runif(1000,-1,1))
pGres=exp(pG)/maxSEA;
pGres=ifelse(pGres>1,1,pGres)

# trade_off
plot(pG,coefSURV(pGres, kappaSEA, sigSEA),type='l',ylab="Survival coefficient",xlab="Growth potential",main="Trade-off at sea")

```

## Toward an optimal value of growth potential

### River growth

With pGsea = pG (correlated)

So there is a disadvantage to have a high growth potential value for river survival, but there is also a size dependent survival in sea and reproductive success. Here we try to show an optimal value should rise from these selective pressures.
We model the lifetime reproductive success of a range of individuals growth potential values.
Here are their size after river summer growth:

```{r, echo=FALSE}

####--- PARAMETERS ---###

#Populations parameters of river growth
b=0.31
dr=0.5 #0.427 #edit lamarins new environmental conditions
Tlr=6
gr=0.208
Tur=24.5
bdens=142.7
lwa=3.804
lwb=0.32
ppercfm=0.12

#Trade-off parameters
#with river trade off
maxRIV=5 # maxRIV maximum growth rate, aded for the incorporation of trade-off growth/survival
sigRIV=3.7 #10 # sigRIV shape of the trade-off function
kappaRIV=0.001 #921.6 # kappaRIV shape of the trade-off function
#without river trade off
maxRIV2=50
sigRIV2=100
kappaRIV2=0.001

#Sea growth parameters
kg=0.003057
wmax=8500
lwa_sea=3.82568
lwb_sea=0.333779
alphaS=2.533333
betaS=-0.524

#Fecundity parameters
aNegg = 0.86
bNegg = 1.63

# Survival in River
SP0=0.9841606*1.0025 #edit buoro
SP1=0.9914398*1.0025 #edit buoro
SP1S=0.9967923*1.002
SP1M=0.9863295*1.002
SPnM=0.9911798*1.002
SPn=0.99775*1.002

####---- Model fitness for a range of pG values (pG = pGsea) - trade-off in river only ----###

#1. ind born 1st april

n=1000
#pG=sort(rnorm(n,0,0.25)) ##careful here gG #if range of pG:sort(rnorm(100000,0,(0.2/sqrt(0.14))))
pG=sort(runif(n,-1,1))
#pG=sort(rnorm(100000,0.15,0.2)) ##careful here gG #if range of
pGres=exp(pG)/maxRIV;
pGres=ifelse(pGres>1,1,pGres)

pGres2=exp(pG)/maxRIV2;
pGres2=ifelse(pGres2>1,1,pGres2)

winit=rep(0.1,n) #initial weight
linit=rep(0.1,n) #initial length
fatinit=rep(0.1,n) #initial fat reserves

#2. river growth april-october

nb_days = 183
#nb_days = 220 #increase nb days because optimum 0.1 instead of 0 (because we missed parr 1+ ? that would stay longer in river and present the higher differences in term of trade-off survival ...)
omega=sum(rep(dr*(15-Tlr)*(1-exp(gr*(15-Tur))), nb_days)) #temperature effect #15 
denseffect=.6 #density effect (adjusted here)
activity=exp(pG) #activity effect - summer:1
#for (t in 1:183) {
  w_parr= (winit^b + b*omega*activity*denseffect/100)^(1/b)
  fat_parr = fatinit + (w_parr-winit)*0.2 
  l_parr = exp(lwa+lwb*log((w_parr-fat_parr)/(1-ppercfm)))
#}#find correct weight in october in simul
plot(w_parr~pG,type='l', xlab="pG",ylab="weight after summer")
plot(fat_parr~pG,type='l', xlab="pG",ylab="fat after summer")
plot(l_parr~pG,type='l', xlab="pG",ylab="size after summer")
```

### River survival

Here is their survival rate after summer (with growth-survival trade-off):
```{r, echo=FALSE}

#3. survival april-october

P_survival_parr=pow(SP0*coefSURV(pGres, kappaRIV, sigRIV),nb_days);
P_survival_parr2=pow(SP02*coefSURV(pGres2, kappaRIV2, sigRIV2),nb_days);

plot(pG,P_survival_parr,type='l',ylab="Survival",xlab="Growth potential",main="Survival summer")
lines(pG,P_survival_parr2, col="red")
legend("bottomright", cex=.8, legend=c("With TO","Without TO"), border=NA,fill=c("black","red"), bty="n")
```

Then, parr decide to migrate to sea next summer and here are their size after winter (before migration):
```{r, echo=FALSE}
#4. growth november-april with decision to migrate to sea

#omega=dr*(15-Tlr)*(1-exp(gr*(15-Tur)))
omega=sum(rep(dr*(11-Tlr)*(1-exp(gr*(11-Tur))),nb_days))
denseffect=.6
activity=exp(pG)*0.725 #smolt
#for (t in 1:183) {
w_smolt= (w_parr^b + b*omega*activity*denseffect/100)^(1/b)
fat_smolt = fat_parr + (w_smolt-w_parr)*0
l_smolt = exp(lwa+lwb*log((w_smolt-fat_smolt)/(1-ppercfm)))
#}#find correct weight in october in simul
plot(w_smolt~pG,type='l', xlab="pG",ylab="weight after winter")
plot(fat_smolt~pG,type='l', xlab="pG",ylab="fat after winter")
plot(l_smolt~pG,type='l', xlab="pG",ylab="size after winter")
```

And their survival rate after winter:
```{r, echo=FALSE}
P_survival_smolt=pow(SP1S*coefSURV(pGres, kappaRIV, sigRIV),nb_days);
P_survival_smolt2=pow(SP1S2*coefSURV(pGres2, kappaRIV2, sigRIV2),nb_days);

plot(pG,P_survival_smolt,type='l',ylab="Survival",xlab="Growth potential",main="Survival winter")
lines(pG,P_survival_smolt2,col="red")
legend("bottomright", cex=.8, legend=c("With TO","Without TO"), border=NA,fill=c("black","red"), bty="n")
```

So over the 1st year in river, the relationship between growth potential and river survival rate is:
```{r, echo=FALSE}
P_survival_river = P_survival_parr*P_survival_smolt
P_survival_river2 = P_survival_parr2*P_survival_smolt2

plot(pG,P_survival_river,type='l',ylab="Survival rate",xlab="Growth potential",main="Survival after one year in river")
lines(pG,P_survival_river2,col="red")
legend("bottomright", cex=.8, legend=c("With TO","Without TO"), border=NA,fill=c("black","red"), bty="n")

```

### Sea growth and survival

Then, fish migrate to sea and can spend around 1 year to grow there:
```{r, echo=FALSE}
#5. sea growth

w_previous= w_smolt
fat_previous= fat_smolt
SP_sea = 1
for (t in 1:(365)) {
  w_sea= w_previous + (kg * w_previous * log(exp(pG) * wmax / w_previous)*1) 
  fat_sea = fat_previous + (w_sea-w_previous)*0.15
  l_sea = exp(lwa_sea+lwb_sea*log((w_sea-fat_sea)/(1-ppercfm)))
  w_previous = w_sea
  fat_previous = fat_sea
  SP_sea = SP_sea * (1 - alphaS*(l_sea/exp(lwa_sea))^(betaS/lwb_sea))^(1/30) #no tradeoff in sea
  
}
plot(w_sea~pG,type='l', xlab="pG",ylab="weight after winter")
plot(fat_sea~pG,type='l', xlab="pG",ylab="fat after winter")
plot(l_sea~pG,type='l', xlab="pG",ylab="size after winter")
```

Survival in sea is dependent of the size and here is the relationship with individual growth potential:
```{r, echo=FALSE}
#sea survival
SP_sea[SP_sea=="NaN"]<-0
plot(pG,SP_sea,type='l',ylab="Survival rate",xlab="Growth potential",main='Survival after one year in sea')
```

### Reproductive success

Finally, if we consider females returning to river to breed, their eggs number produced depend on their weight and here is the relationship with individual growth potential:
```{r, echo=FALSE}
#6. Neggs considering all female reproduce

neggs = exp(aNegg * log(w_sea) + bNegg)
plot(pG,neggs,type='l',ylab="Neggs",xlab="Growth potential",main="Eggs number by female")
```

### Fitness

```{r, echo=FALSE}
#total fitness
fitness= P_survival_river * SP_sea * neggs
fitness2= P_survival_river2 * SP_sea * neggs

## FIGURE 2 A ##
plot(NULL,ylab="LRS (Lifetime Recruitment Success)",xlab="Growth potential", xlim=c(-1,1), ylim=c(0,5))
lines(pG[1:6000],fitness2[1:6000], lty=2, lwd=3)
lines(pG,fitness,lwd=3, lty=1)

legend("topright", cex=.8, legend=c("With Trade-off","Without Trade-off"), border=NA,lty=c(1,2), bty="n")

```



